Online Variable Elimination for Credal Polytrees

### 2017-03-01 paper.tex
replaced \include by \input
First change

\documentclass[twoside,11pt]{article}
\usepackage{isipta}
%% Comment these two lines if you don't need UTF8
\usepackage[utf8]{inputenc}
\inputencoding{utf8} 
% Note that pgm.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
% It also sets the bibliographystyle 
%% Put here the import commands of the packages you need and your custom commands 
\usepackage{hyperref,color,soul,booktabs,bm,algpseudocode,algorithm,tikz,pgfplots}
\usepackage{xargs}                      % Use more than one optional parameter in a new commands
%\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
% TIKZ for drawing
\usetikzlibrary{shapes.geometric} % for diamond nodes shape
\usepgflibrary{shapes.arrows} % for latex arrow shape
\newtheorem{mydef}[theorem]{Definition}
\newtheorem{myex}[theorem]{Example}
\setulcolor{blue}
\newcommand{\BibTeX}{\textsc{B\kern-0.1emi\kern-0.017emb}\kern-0.15em\TeX}
% Running title and authors 
\ShortHeadings{ISIPTA '17: Author Instructions}{Antonucci et al.} 
%\pgmheading{1}{2000}{1-48}{4/00}{10/00}{Professorson and Teacherman}
%\firstpageno{10}
\usepackage{todonotes}
\presetkeys{todonotes}{fancyline, color=blue!30}{}
%\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
%\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
%\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
%\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
%\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
%\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
\begin{document}
% Title and authors
\title{Online Variable Elimination for Credal Polytrees}
\author{\name Jasper De Bock \email jasper.debock@ugent.be\\
\addr University of Ghent\\
Ghent (Belgium)\\
\AND
\name David Huber \email david@idsia.ch\\
\name Alessandro Antonucci \email alessandro@idsia.ch\\
\addr Istituto Dalle Molle di Studi Sull'Intelligenza Artificiale (IDSIA)\\
Lugano (Swizterland)}
\maketitle
\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
We propose a variable-elimination algorithm for exact inference in singly connected credal networks with strong independence. Compared to earlier works in this direction, the necessary extensive specification of the local models and the convexification are performed in an online way. This might produce considerable savings in memory and, for convexification only, time. Moreover, we show that with singly connected networks the convexification of the intermediate results of the inference can be achieved before the elimination step in a space with the same dimensionality of the variable to eliminate. This prevents issues related to convex hulls in high dimensions. Despite the NP-hardness of the inference even in the case of singly connected topologies, the experiments on a benchmark of randomly generated credal polytrees shows that exact inference can be achieved in models up to xxx variables if the number xxx. A further speed-up, at the price of an approximation, is achieved by rounding the values of the extreme points before the convexification, while an extension to general topologies can be achieved by loopset conditioning.
\end{abstract}
\begin{keywords}
Credal networks; convex hull; variable elimination; cutset conditioning.
\end{keywords}
\include{intro}
\include{basics}
\include{VEdummy}
\include{VEsmart}
\include{example}
%\include{experiments}
\section{Conclusions and Outlooks}
Mention that we might explore other (more complex) inference task such as the computation of the probability of evidence as well as the maximum a posteriori hypothesis task (MAP), which in the credal setting can be formulated in different ways.
\bibliography{biblio}
\end{document}

>>>>

\documentclass[twoside,11pt]{article}
\usepackage{isipta}
%% Comment these two lines if you don't need UTF8
\usepackage[utf8]{inputenc}
\inputencoding{utf8} 
% Note that pgm.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
% It also sets the bibliographystyle 
%% Put here the import commands of the packages you need and your custom commands 
\usepackage{hyperref,color,soul,booktabs,bm,algpseudocode,algorithm,tikz,pgfplots}
\usepackage{xargs}                      % Use more than one optional parameter in a new commands
%\usepackage[pdftex,dvipsnames]{xcolor}  % Coloured text etc.
% TIKZ for drawing
\usetikzlibrary{shapes.geometric} % for diamond nodes shape
\usepgflibrary{shapes.arrows} % for latex arrow shape
\newtheorem{mydef}[theorem]{Definition}
\newtheorem{myex}[theorem]{Example}
\setulcolor{blue}
\newcommand{\BibTeX}{\textsc{B\kern-0.1emi\kern-0.017emb}\kern-0.15em\TeX}
% Running title and authors 
\ShortHeadings{ISIPTA '17: Author Instructions}{Antonucci et al.} 
%\pgmheading{1}{2000}{1-48}{4/00}{10/00}{Professorson and Teacherman}
%\firstpageno{10}
\usepackage{todonotes}
\presetkeys{todonotes}{fancyline, color=blue!30}{}
%\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
%\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
%\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
%\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
%\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
%\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
\begin{document}
% Title and authors
\title{Online Variable Elimination for Credal Polytrees}
\author{\name Jasper De Bock \email jasper.debock@ugent.be\\
\addr Ghent University, IDLab\\
Belgium\\
\AND
\name David Huber \email david@idsia.ch\\
\name Alessandro Antonucci \email alessandro@idsia.ch\\
\addr Istituto Dalle Molle di Studi Sull'Intelligenza Artificiale (IDSIA)\\
Lugano (Switzerland)}
\maketitle
\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
We propose a variable-elimination algorithm for exact inference in singly connected credal networks with strong independence. Compared to earlier works in this direction, the necessary extensive specification of the local models and the convexification are performed in an online way. This might produce considerable savings in memory and, for convexification only, time. Moreover, we show that with singly connected networks the convexification of the intermediate results of the inference can be achieved before the elimination step in a space with the same dimensionality of the variable to eliminate. This prevents issues related to convex hulls in high dimensions. Despite the NP-hardness of the inference even in the case of singly connected topologies, the experiments on a benchmark of randomly generated credal polytrees shows that exact inference can be achieved in models up to xxx variables if the number xxx. A further speed-up, at the price of an approximation, is achieved by rounding the values of the extreme points before the convexification, while an extension to general topologies can be achieved by loopset conditioning.
\end{abstract}
\begin{keywords}
Credal networks; convex hull; variable elimination; cutset conditioning.
\end{keywords}
\input{intro}
\input{basics}
\input{VEdummy}
\input{VEsmart}
\input{example}
%\input{experiments}
\section{Conclusions and Outlooks}
Let me see. Mention that we might explore other (more complex) inference task such as the computation of the probability of evidence as well as the maximum a posteriori hypothesis task (MAP), which in the credal setting can be formulated in different ways.
\bibliography{biblio}
\end{document}
